Bird species composition in coastal urban habitats

### 2021-01-12 Ms_HabitatAves.Rmd
avance discusion

Some species with seasonal differences are related to migratory behaviour, or specific nesting habitat requierements (**Leucophaeus modestus** in @cikutovic1988gonadal, **Sephanoides sephanoides**).

>>>>

Some species with seasonal differences are related to migratory behaviour, or specific nesting habitat requierements (**Leucophaeus modestus** that nest only in the Atacama desert: @cikutovic1988gonadal and @aguilar2016unusual, **Sephanoides sephanoides**).
